PK object batch mode trial

### 2023-09-08 data-raw/batchMode_trial_gpm.Rmd
Redesigned the convert_time() function by adding a convert_time_table() sub-function which pre-generates a conversion table for all time units. Utilizes updated lubridate functions for conversions.

```{r single_fit}
# Pooled
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

@@

my_pk <- do_prefit(my_pk) # needs reframe somewhere
# Timing for normal fit sapply
{
  start_t <- Sys.time()
  my_pk <- do_fit(my_pk, n_cores = 6)
  round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
}
# my_pk <- do_fit(my_pk)

plot(my_pk, method = "L-BFGS-B",
     n_interp = 12) -> pl

@@

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "get_tkstats",
                  # descendents = FALSE,
                  ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)

@@

>>>>

```{r single_fit}
# Pooled
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

my_pk <- do_prefit(my_pk) # needs reframe somewhere
# Timing for normal fit sapply
{
  start_t <- Sys.time()
  my_pk <- do_fit(my_pk, n_cores = 6)
  round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
}
# my_pk <- do_fit(my_pk)
{
  start_t <- Sys.time()
  my_pk_time_scaling <- do_fit(my_pk_time_scaling, n_cores = 10)
  round(Sys.time() - start_t, 3) # w/ Time scaling 36mins!
}

profvis::profvis(
  plot(my_pk,
     n_interp = 10)
)

plot(my_pk, method = "L-BFGS-B",
     n_interp = 5) -> pl

@@

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "time_units",
                  # descendents = FALSE,
                  # ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)

@@

### Time table (refactoring convert_time)

```{r convert_time_table}

expand_grid(TimeA = time_units, TimeB = time_units) %>%
  mutate(A_fun = paste0("d", TimeA), B_fun = paste0("d", TimeB)) %>%
  rowwise() %>%
  mutate(conversion = 
           do.call(A_fun, list(1))/do.call(B_fun, list(1))) %>%
  dplyr::select(!c(A_fun, B_fun))
